New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2023-01-19 paper/paper.Rmd
why not R expanded

\textcolor{blue}{One might implement such an interactive interface in R, for example using `shiny` [@shinym], with `plotly` [@plotly] drawing. It could be possible with `rgl` [@rgl] but this package is focused on 3D, not the arbitrary $p$-D of tours. The primary tool needed is the tracking of the cursor position in small increments and it is not readily available in R. The `plotly` package is designed to add on to `ggplot2` graphics, not to be a programmable interactive graphics system. It would have been possible with the `cranvas` system [@cranvas] or `rJava` [@rJava] but neither has a graphics toolkit that operates across platforms today. What we have chosen to do is to use the interactivity of Mathematica to experiment, and to implement as an animation in the `tourr` [@tourr] package. There is hope that better interactivity will be available for R soon, perhaps in javascript, which might allow for experimentation to develop new techniques as available in Mathematica.}

@@

\textcolor{blue}{Di will explain what part and why is difficult in R, also check grammar}

>>>>

\textcolor{blue}{Within R, the natural implementation for an interactive interface would use} `shiny` [@shinym] with `plotly` [@plotly] drawing. However, the `plotly` package is designed to add on to `ggplot2` graphics, not to be a programmable interactive graphics system. It lacks capability to implement the primary tool needed for a manual tour, that is the tracking of the cursor position in small increments. In theory, the historical `locator()` function of base R should provide the necessary capability, but it's behavior is not consistent between graphical devices. The cursor position control is possible with `rgl` [@rgl] but this package is focused on 3D, not the arbitrary dimension of tours. The level of interactivity would have been possible with the `cranvas` system [@cranvas] or `rJava` [@rJava] but neither has a graphics toolkit that currently operates across platforms.  What we have chosen to do is to use the interactivity of Mathematica to experiment, and to implement as an animation in the `tourr` [@tourr] package. There is hope that better interactivity will be available for R soon, perhaps in javascript [e.g. @langevitour, @detourr], which might allow for the  experimentation to develop new techniques.

@@

### 2023-01-19 paper/paper.tex
why not R expanded

\textcolor{blue}{One might implement such an interactive interface in R, for example using `shiny` [@shinym], with `plotly` [@plotly] drawing. It could be possible with `rgl` [@rgl] but this package is focused on 3D, not the arbitrary $p$-D of tours. The primary tool needed is the tracking of the cursor position in small increments and it is not readily available in R. The `plotly` package is designed to add on to `ggplot2` graphics, not to be a programmable interactive graphics system. It would have been possible with the `cranvas` system [@cranvas] or `rJava` [@rJava] but neither has a graphics toolkit that operates across platforms today. What we have chosen to do is to use the interactivity of Mathematica to experiment, and to implement as an animation in the `tourr` [@tourr] package. There is hope that better interactivity will be available for R soon, perhaps in javascript, which might allow for experimentation to develop new techniques as available in Mathematica.}

>>>>

\textcolor{blue}{Within R, the natural implementation for an interactive interface would use}
\texttt{shiny} \citep{shinym} with \texttt{plotly} \citep{plotly}
drawing. However, the \texttt{plotly} package is designed to add on to
\texttt{ggplot2} graphics, not to be a programmable interactive graphics
system. It lacks capability to implement the primary tool needed for a
manual tour, that is the tracking of the cursor position in small
increments. In theory, the historical \texttt{locator()} function of
base R should provide the necessary capability, but it's behavior is not
consistent between graphical devices. The cursor position control is
possible with \texttt{rgl} \citep{rgl} but this package is focused on
3D, not the arbitrary dimension of tours. The level of interactivity
would have been possible with the \texttt{cranvas} system
\citep{cranvas} or \texttt{rJava} \citep{rJava} but neither has a
graphics toolkit that currently operates across platforms. What we have
chosen to do is to use the interactivity of Mathematica to experiment,
and to implement as an animation in the \texttt{tourr} \citep{tourr}
package. There is hope that better interactivity will be available for R
soon, perhaps in javascript \citep[e.g.][\citet{detourr}]{langevitour},
which might allow for the experimentation to develop new techniques.
